---
title: "CaseStudy10_LeeMessaGarza"
authors: "Brian Less, Araya Messa, Tony Garza"
date: "July 24, 2016"
output: 
  html_document:
    keep_md: TRUE
---
<<<<<<< HEAD
# Introduction

### Add introduction here

## Project Setup and Required Packages

```{r, message=FALSE, results="hide"}
setwd("C:/Users/thisi/OneDrive/git_repositories/CaseStudy10_LeeMessaGarza")
library(fpp) # must install.packages("fpp", repos = "https://cran.revolutionanalytics.com")
library(foreach) # must install.packages("foreach", repos = "https://cran.revolutionanalytics.com")
```

## Import and Data Cleanup

```{r}
source("ImportAndCleanupData.R")
```

Importing and tidying data from the files: ImportedAsIsDataChulwalar.csv, ImportedPlanDataChulwalar.csv, and ImportedIndicatorsChulwalar.csv.

## Defined Objects
```{r}
source("DefinedObjects.R")
```

All Objects loaded for exploration and analysis

# Exploration of Chulwalar Data

## Definition of the Indicators and Their Correlation with the Basic Data

### Monthly Change in Export Price Index (CEPI)

```{r}
plot(CEPI, main="CEPI")

cor(TotalAsIs, CEPI)
cor(EfakAsIs , CEPI)
cor(WugeAsIs, CEPI)
cor(TotalEtelAsIs, CEPI)
cor(BlueEtelAsIs , CEPI)
cor(RedEtelAsIs , CEPI)
```

The CEPI correlates very well with the efak exports.

### Monthly Satisfaction Index (SI) government based data

```{r}
plot(SIGov, main="SIGov")

cor(TotalAsIs, SIGov)
cor(EfakAsIs , SIGov)
cor(WugeAsIs, SIGov)
cor(TotalEtelAsIs, SIGov)
cor(BlueEtelAsIs , SIGov)
cor(RedEtelAsIs , SIGov)
```

The Satisfaction Index does not show any particular correlation with any of the exports data.

### Average monthly temperatures in Chulwalar

```{r}
plot(Temperature, main="Temperature")

cor(TotalAsIs, Temperature)
cor(EfakAsIs , Temperature)
cor(WugeAsIs, Temperature)
cor(TotalEtelAsIs, Temperature)
cor(BlueEtelAsIs , Temperature)
cor(RedEtelAsIs , Temperature)
```

The temperatures have a negative correlation, exports increase in the colder months. However, the relationship is only stronger with blue Etels.

### Monthly births in Chulwalar

```{r}
plot(Births, main="Births")

cor(TotalAsIs, Births)
cor(EfakAsIs , Births)
cor(WugeAsIs, Births)
cor(TotalEtelAsIs, Births)
cor(BlueEtelAsIs , Births)
cor(RedEtelAsIs , Births)
```

The consideration by Chulwalar's experts was that expecting new parents to try to export more products to pay for the cost of a new child. However, this could not be confirmed.  

### Monthly Satisfaction Index (SI) external index 

```{r}
plot(SIExtern, main="SIExtern")

cor(TotalAsIs, SIExtern)
cor(EfakAsIs , SIExtern)
cor(WugeAsIs, SIExtern)
cor(TotalEtelAsIs, SIExtern)
cor(BlueEtelAsIs , SIExtern)
cor(RedEtelAsIs , SIExtern)
```

This indicator also has a high correlation with Efak exports. 

### Yearly Exports from Urbano

```{r}
plot(UrbanoExports, main="UrbanoExports")

cor(TotalAsIs, UrbanoExports)
cor(EfakAsIs , UrbanoExports)
cor(WugeAsIs, UrbanoExports)
cor(TotalEtelAsIs, UrbanoExports)
cor(BlueEtelAsIs , UrbanoExports)
cor(RedEtelAsIs , UrbanoExports)
```

This indicator also has a high correlation with Efak exports. The Wuge exports also show a correlation. Unfortunatly it was not possible to find other useful indicators based on exports from Urbano, due to possible informers being very restrictive with information. 

### Yearly number of Globalisation Party members in Chulwalar

```{r}
plot(GlobalisationPartyMembers, main="GlobalisationPartyMembers")

cor(TotalAsIs, GlobalisationPartyMembers)
cor(EfakAsIs , GlobalisationPartyMembers)
cor(WugeAsIs, GlobalisationPartyMembers)
cor(TotalEtelAsIs, GlobalisationPartyMembers)
cor(BlueEtelAsIs , GlobalisationPartyMembers)
cor(RedEtelAsIs , GlobalisationPartyMembers)
```

There is a similar picture here to that of Urbano Exports. It should however be noted that there is a continuos growth here and that the yearly view could lead to the data appearing to correlate, although this could just be due to an increase in trend. Although this could also be true for the Urbano Exports, the trend seems logical due to the Chulwalar's exports growing in accordance with the Urbano's Exports.

### Monthly Average Export Price Index for Chulwalar

```{r}
plot(AEPI, main="AEPI")

cor(TotalAsIs, AEPI)
cor(EfakAsIs , AEPI)
cor(WugeAsIs, AEPI)
cor(TotalEtelAsIs, AEPI)
cor(BlueEtelAsIs , AEPI)
cor(RedEtelAsIs , AEPI)
```

The continuous growth leads to a good correlation here too.

### Monthly Producer Price Index (PPI) for Etel in Chulwalar

```{r}
plot(PPIEtel, main="PPIEtel")

cor(TotalAsIs, PPIEtel)
cor(EfakAsIs , PPIEtel)
cor(WugeAsIs, PPIEtel)
cor(TotalEtelAsIs, PPIEtel)
cor(BlueEtelAsIs , PPIEtel)
cor(RedEtelAsIs , PPIEtel)
```

This indicator does not give the expected results. It does not show any correlation worth mentioning, not even with the Etel segment. 

### National Holidays

```{r}
plot(NationalHolidays, main="NationalHolidays")

cor(TotalAsIs, NationalHolidays)
cor(EfakAsIs , NationalHolidays)
cor(WugeAsIs, NationalHolidays)
cor(TotalEtelAsIs, NationalHolidays)
cor(BlueEtelAsIs , NationalHolidays)
cor(RedEtelAsIs , NationalHolidays)
```

The months April and December do not correlate well with the exports data. However later tests will show that these are worth considering. The missing correlation is just due to the sparse structure of the NationalHolidays time series.

### Chulwalar Index (Total value of all companies in Chulwalar)

```{r}
plot(ChulwalarIndex, main="ChulwalarIndex")

cor(TotalAsIs, ChulwalarIndex)
cor(EfakAsIs , ChulwalarIndex)
cor(WugeAsIs, ChulwalarIndex)
cor(TotalEtelAsIs, ChulwalarIndex)
cor(BlueEtelAsIs , ChulwalarIndex)
cor(RedEtelAsIs , ChulwalarIndex)
```

No particular findings.

### Monthly Inflation rate in Chulwalar

```{r}
plot(Inflation, main="Inflation")

cor(TotalAsIs, Inflation)
cor(EfakAsIs , Inflation)
cor(WugeAsIs, Inflation)
cor(TotalEtelAsIs, Inflation)
cor(BlueEtelAsIs , Inflation)
cor(RedEtelAsIs , Inflation)
```

No particular findings.

### Proposed spending for National Holidays

```{r}
plot(IndependenceDayPresents, main="IndependenceDayPresents")

cor(TotalAsIs, IndependenceDayPresents)
cor(EfakAsIs , IndependenceDayPresents)
cor(WugeAsIs, IndependenceDayPresents)
cor(TotalEtelAsIs, IndependenceDayPresents)
cor(BlueEtelAsIs , IndependenceDayPresents)
cor(RedEtelAsIs , IndependenceDayPresents)
```

No particular findings.

### Influence of National Holiday

```{r}
plot(InfluenceNationalHolidays, main="InfluenceNationalHolidays")

cor(TotalAsIs, InfluenceNationalHolidays)
cor(EfakAsIs , InfluenceNationalHolidays)
cor(WugeAsIs, InfluenceNationalHolidays)
cor(TotalEtelAsIs, InfluenceNationalHolidays)
cor(BlueEtelAsIs , InfluenceNationalHolidays)
cor(RedEtelAsIs , InfluenceNationalHolidays)
```

This indicator is an experiment where the influence of National Holidays is extended into the months leading up to the holiday. However later tests show that this indicator is no better for forecasting than the orignial National Holidays indicator.   





# Analysis

## Basic Plots of the As Is and Planned Data

```{r, echo=FALSE}
=======
# Import and Prepare Data

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fpp)



#################################################################################
#   1.1 Import the exports data and the indicators                              #
#################################################################################

### !!! In order to test the script, it is necessary to change the three
### file paths. The files have been sent together with the script!!!

# The Export data for Chulwalar   are in two .csv files.
# One file for the as is data: ImportedAsIsDataChulwalar.csv
# and another one for the plan data: ImportedPlanDataChulwalar.csv

setwd("~/Dropbox/SMUDataScienceClass/1st class/Week 10/CaseStudy10_LeeMessaGarza")

ImportedAsIsData <- read.csv("ImportedAsIsDataChulwalar.csv", header = F, sep=";", fill = T) #chose ImportedAsIsDataChulwalar.csv

ImportedPlanData <- read.csv("ImportedPlanDataChulwalar.csv", header = F, sep=";", fill = T) #chose ImportedPlanDataChulwalar.csv



# The indicators data is also in a file: ImportedIndicatorsChulwalar.csv
ImportedIndicators <- read.csv("ImportedIndicatorsChulwalar.csv", header = F, sep=";", fill = T) # chose ImportedIndicatorsChulwalar.csv


TotalAsIsVector <- c(ImportedAsIsData [2:13,2],ImportedAsIsData [2:13,3],ImportedAsIsData [2:13,4],ImportedAsIsData [2:13,5],ImportedAsIsData [2:13,6],ImportedAsIsData [2:13,7])
EfakAsIsVector <- c(ImportedAsIsData [16:27,2],ImportedAsIsData [16:27,3],ImportedAsIsData [16:27,4],ImportedAsIsData [16:27,5],ImportedAsIsData [16:27,6],ImportedAsIsData [16:27,7])
WugeAsIsVector <- c(ImportedAsIsData [30:41,2],ImportedAsIsData [30:41,3],ImportedAsIsData [30:41,4],ImportedAsIsData [30:41,5],ImportedAsIsData [30:41,6],ImportedAsIsData [30:41,7])
TotalEtelAsIsVector <- c(ImportedAsIsData [44:55,2],ImportedAsIsData [44:55,3],ImportedAsIsData [44:55,4],ImportedAsIsData [44:55,5],ImportedAsIsData [44:55,6],ImportedAsIsData [44:55,7])
BlueEtelAsIsVector <- c(ImportedAsIsData [58:69,2],ImportedAsIsData [58:69,3],ImportedAsIsData [58:69,4],ImportedAsIsData [58:69,5],ImportedAsIsData [58:69,6],ImportedAsIsData [58:69,7])
RedEtelAsIsVector <- c(ImportedAsIsData [72:83,2],ImportedAsIsData [72:83,3],ImportedAsIsData [72:83,4],ImportedAsIsData [72:83,5],ImportedAsIsData [72:83,6],ImportedAsIsData [72:83,7])
YearAsIsVector <- c(ImportedAsIsData [86,2],ImportedAsIsData [86,3],ImportedAsIsData [86,4],ImportedAsIsData [86,5],ImportedAsIsData [86,6],ImportedAsIsData [86,7])
TotalAsIsVector_2014 <- c(ImportedAsIsData[2:13,8])

PlanVector <- c(ImportedPlanData[2:13,2],ImportedPlanData[2:13,3],ImportedPlanData[2:13,4],ImportedPlanData[2:13,5],ImportedPlanData[2:13,6],ImportedPlanData[2:13,7])
EfakPlanVector <- c(ImportedPlanData[16:27,2],ImportedPlanData[16:27,3],ImportedPlanData[16:27,4],ImportedPlanData[16:27,5],ImportedPlanData[16:27,6],ImportedPlanData[16:27,7])
WugePlanVector <- c(ImportedPlanData[30:41,2],ImportedPlanData[30:41,3],ImportedPlanData[30:41,4],ImportedPlanData[30:41,5],ImportedPlanData[30:41,6],ImportedPlanData[30:41,7])
TotalEtelPlanVector <- c(ImportedPlanData[44:55,2],ImportedPlanData[44:55,3],ImportedPlanData[44:55,4],ImportedPlanData[44:55,5],ImportedPlanData[44:55,6],ImportedPlanData[44:55,7])
BlueEtelPlanVector <- c(ImportedPlanData[58:69,2],ImportedPlanData[58:69,3],ImportedPlanData[58:69,4],ImportedPlanData[58:69,5],ImportedPlanData[58:69,6],ImportedPlanData[58:69,7])
RedEtelPlanVector <- c(ImportedPlanData[72:83,2],ImportedPlanData[72:83,3],ImportedPlanData[72:83,4],ImportedPlanData[72:83,5],ImportedPlanData[72:83,6],ImportedPlanData[72:83,7])
YearPlanVector <- c(ImportedPlanData[86,2],ImportedPlanData[86,3],ImportedPlanData[86,4],ImportedPlanData[86,5],ImportedPlanData[86,6],ImportedPlanData[86,7])
PlanVector_2014 <- c(ImportedPlanData[2:13,8])

# The data is saved as a vector and needs to be converted into a time series

TotalAsIs<- ts(TotalAsIsVector , start=c(2008,1), end=c(2013,12), frequency=12)
EfakAsIs <- ts(EfakAsIsVector , start=c(2008,1), end=c(2013,12), frequency=12)
WugeAsIs <- ts(WugeAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalEtelAsIs<- ts(TotalEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
BlueEtelAsIs <- ts(BlueEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
RedEtelAsIs <- ts(RedEtelAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
YearAsIs <- ts(YearAsIsVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalAsIs_2014 <- ts(TotalAsIsVector_2014, start=c(2014,1), end=c(2014,12), frequency=12)

TotalPlan <- ts(PlanVector , start=c(2008,1), end=c(2013,12), frequency=12)
EfakPlan <- ts(EfakPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
WugePlan <- ts(WugePlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalEtelPlan <- ts(TotalEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
BlueEtelPlan <- ts(BlueEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
RedEtelPlan <- ts(RedEtelPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
YearPlan <- ts(YearPlanVector, start=c(2008,1), end=c(2013,12), frequency=12)
TotalPlan_2014 <- ts(PlanVector_2014, start=c(2014,1), end=c(2014,12), frequency=12)

# Call up the time series to check everything has worked.

TotalAsIs
EfakAsIs
WugeAsIs
TotalEtelAsIs
BlueEtelAsIs 
RedEtelAsIs 
YearAsIs
TotalAsIs_2014

TotalPlan
EfakPlan
WugePlan 
TotalEtelPlan
BlueEtelPlan
RedEtelPlan
YearPlan
TotalPlan_2014

```

##Plot Them
```{r}
>>>>>>> 64ead25a7a64e91a2fa8df2659f00922228ca2ef
par(mfrow=c(3,2))

plot(TotalAsIs, col="black", main="TotalAsIs")
plot(EfakAsIs , col="red",main="EfakAsIs")
plot(WugeAsIs, col="blue", main="WugeAsIs")
plot(TotalEtelAsIs, col="green",main="TotalEtelAsIs")
plot(BlueEtelAsIs, col="orange", main="BlueEtelAsIs")
plot(RedEtelAsIs, col="purple", main="RedEtelAsIs")
<<<<<<< HEAD

=======
>>>>>>> 64ead25a7a64e91a2fa8df2659f00922228ca2ef
plot(TotalPlan , col="black", main="TotalPlan")
plot(EfakPlan , col="red",main="EfakPlan")
plot(WugePlan, col="blue", main="WugePlan")
plot(TotalEtelPlan, col="green",main="TotalEtelPlan")
plot(BlueEtelPlan, col="orange", main="BlueEtelPlan")
plot(RedEtelPlan, col="purple", main="RedEtelPlan")
```

<<<<<<< HEAD
## Correlation Between As Is and Planned Data

=======
# Brian Portion: Test Correlation/Model
>>>>>>> 64ead25a7a64e91a2fa8df2659f00922228ca2ef
```{r}
cor(TotalAsIs, TotalPlan )
cor(EfakAsIs , EfakPlan)
cor(WugeAsIs, WugePlan)
cor(TotalEtelAsIs, TotalEtelPlan)
cor(BlueEtelAsIs , BlueEtelPlan)
cor(RedEtelAsIs , RedEtelPlan)
cor(YearAsIs, YearPlan)
<<<<<<< HEAD

=======
TotalAsIs_lm <- lm(TotalAsIs ~ TotalPlan , data = TotalAsIs)
summary(TotalAsIs_lm)

TotalAsIs_tslm <- tslm(TotalAsIs ~ TotalPlan )
summary(TotalAsIs_tslm)

# National Holidays
NationalHolidaysVector <- c(ImportedIndicators[170:181,2],ImportedIndicators[170:181,3],ImportedIndicators[170:181,4],ImportedIndicators[170:181,5],ImportedIndicators[170:181,6],ImportedIndicators[170:181,7])
NationalHolidays <- ts(NationalHolidaysVector, start=c(2008,1), end=c(2013,12), frequency=12)
plot(NationalHolidays, main="NationalHolidays")

cor(TotalAsIs, NationalHolidays)
cor(EfakAsIs , NationalHolidays)
cor(WugeAsIs, NationalHolidays)
cor(TotalEtelAsIs, NationalHolidays)
cor(BlueEtelAsIs , NationalHolidays)
cor(RedEtelAsIs , NationalHolidays)

# The months April and December do not correlate well with the exports data. 
# However later tests will show that these are worth considering. 
# The missing correlation is just due to the sparse structure of the NationalHolidays time series.
>>>>>>> 64ead25a7a64e91a2fa8df2659f00922228ca2ef
```

# Tony's Portion: Forecasting Models
```{r}
#################################################################################
#  7.1 Exponential Smoothing                                                    #
#################################################################################

# Exponential Smoothing uses past values to calculate a forecast. The strength 
# with which each value influences the forecast is weakened with help of a 
# smoothing parameter. Thus we are dealing with a weighted average, whose 
# values fade out the longer ago they were in the past.

#################################################################################
#  7.1.1 Simple expontential smoothing                                          #
#################################################################################

# Formula: ses(). It must be decided if alpha (the smoothing parameter
# should be automatically calculated. If initial=simple, the alpha value can 
# be set to any chosen value, if initial=optimal (or nothing, as this is the 
# default), alpha will be set to the optimal value based on ets().
# h=12 gives the number of cycles for the forecast.

Model_ses <- ses(TotalAsIs, h=12)
summary(Model_ses)
plot(Model_ses)

# The Akaike's Information Criterion(AIC/AICc) or the Bayesian Information 
# Criterion (BIC) should be at minimum.

plot(Model_ses, plot.conf=FALSE, ylab="Exports Chulwalar  )", xlab="Year", main="", fcol="white", type="o")
lines(fitted(Model_ses), col="green", type="o")
lines(Model_ses$mean, col="blue", type="o")
legend("topleft",lty=1, col=c(1,"green"), c("data", expression(alpha == 0.671)),pch=1)


#################################################################################
#  7.1.2 Holt's linear trend method                                             #
#################################################################################

# Holt added to the model in order to forecast using trends as well.
# For this it is necessary to add a beta, which determines the trend.
# If neither alpha nor beta is stated, both parameters will be optimised
# using ets(). 

Model_holt_1 <- holt(TotalAsIs,h=12)
summary(Model_holt_1)
plot(Model_holt_1)

# The trend is exponential if the intercepts(level) and the gradient (slope) are
# multiplied with eachother. The values are worse. As the Beta was very low in 
# the optimisation, the forecast is very similar to the ses() model. 


Model_holt_2<- holt(TotalAsIs, exponential=TRUE,h=12)
summary(Model_holt_2)
plot(Model_holt_2)

# As such simple trends tend to forecast the future to positively, we have added
# a dampener.
# Similar values to that of Model_holt_1 

Model_holt_3 <- holt(TotalAsIs, damped=TRUE,h=12)
summary(Model_holt_3)
plot(Model_holt_3)

# This also works for exponential trends. 
# The values remain worse. 

Model_holt_4 <- holt(TotalAsIs, exponential=TRUE, damped=TRUE,h=12)
summary(Model_holt_4)
plot(Model_holt_4)


# level and slope can be plotted individually for each model. 
plot(Model_holt_1$model$state)
plot(Model_holt_2$model$state)
plot(Model_holt_3$model$state)
plot(Model_holt_4$model$state)

plot(Model_holt_1, plot.conf=FALSE, ylab="Exports Chulwalar  )", xlab="Year", main="", fcol="white", type="o")
lines(fitted(Model_ses), col="purple", type="o")
lines(fitted(Model_holt_1), col="blue", type="o")
lines(fitted(Model_holt_2), col="red", type="o")
lines(fitted(Model_holt_3), col="green", type="o")
lines(fitted(Model_holt_4), col="orange", type="o")
lines(Model_ses$mean, col="purple", type="o")
lines(Model_holt_1$mean, col="blue", type="o")
lines(Model_holt_2$mean, col="red", type="o")
lines(Model_holt_3$mean, col="green", type="o")
lines(Model_holt_4$mean, col="orange", type="o")
legend("topleft",lty=1, col=c(1,"purple","blue","red","green","orange"), c("data", "SES","Holts auto", "Exponential", "Additive Damped", "Multiplicative Damped"),pch=1)

# As these forecasts are not very convincing at the moment, there is no need 
# to export the data.
#################################################################################
#  7.1.3 Holt-Winter's seasonal method                                          #
#################################################################################

# Holt and Winters have expanded Holt's model further to include the
# seasonality aspect. The parameter gamma, which is for smoothing the
# seasonality, was added to achieve this. The values are better than 
# the models without seasonality. This logical matches our results from the regression approaches, 
# the data is strongly influenced by seasonality. 
# In the following model, none of the parameters are given so that they
# will be optimised automatically. There are two models: one using
# an additive error model method and one using a multiplicative error model.

Model_hw_1 <- hw(TotalAsIs ,seasonal="additive",h=12)
summary(Model_hw_1)
plot(Model_hw_1)
#     AIC     AICc      BIC 
#2127.984 2137.875 2164.411 

Model_hw_2 <- hw(TotalAsIs ,seasonal="multiplicative",h=12)
summary(Model_hw_2)
plot(Model_hw_2)
#     AIC     AICc      BIC 
#2137.673 2147.564 2174.100 

# The additive model gives slightly better results than the multiplicative model.

plot(Model_hw_1, ylab="Exports Chulwalar  ", plot.conf=FALSE, type="o", fcol="white", xlab="Year")
lines(fitted(Model_hw_1), col="red", lty=2)
lines(fitted(Model_hw_2), col="green", lty=2)
lines(Model_hw_1$mean, type="o", col="red")
lines(Model_hw_2$mean, type="o", col="green")
legend("topleft",lty=1, pch=1, col=1:3, c("data","Holt Winters' Additive","Holt Winters' Multiplicative"))
```

### SES AIC:       2230.058
### SES RMSE:    609507.0
### HOLT AIC:      2235.888
### HOLT RMSE:   608787.2
### HOLT_E AIC:    2253.216
### HOLT_E RMSE: 609906.7
### HW_A AIC:     2124.856 HW Additive Model said to be best choice
### HW_A RMSE:  241685.0
### HW_M AIC:     2128.303
### HW_M RMSE:  235296.6
### Provided case says the HW additive model gives slightly better results than the multiplicative model. However, one can make a case for the multiplicative model as AICs are similar and the RMSE for the multiplicative model is 3% less than the additive.

# Araya Portion: How well does forecast meet planned exports? (May want to try this for both the HW_A and HW_M). I believe we should also try with Brian's portion as well, once he has completed it.